% resume.tex
%
%
\documentclass[10pt]{article}
\usepackage{fullpage1}	
\usepackage{atbeginend}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage[pdftex]{hyperref}
\textheight=9.1in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\newenvironment{itemize*}%
  {\begin{itemize}%
    \setlength{\itemsep}{0pt}%
    \setlength{\parskip}{0pt}%
	}
  {\end{itemize}}
\newenvironment{description*}%
  {\begin{description}%
   \setlength{\itemsep}{0pt}%
   \setlength{\parskip}{0pt}%
	}
  {\end{description}}
\begin{document}

\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large{Rahul Garg}}  & \\
Staff Research Scientist &  Ph:(206) 708 5975\\
Google Inc. & \href{http://www.cs.washington.edu/homes/rahul}{http://www.rahulgarg.com}\\ 
1600 Amphitheatre Parkway, Mountain View, CA 94043 &  Email: \href{mailto:rahul.gargrahul@gmail.com}{rahul.gargrahul@gmail.com}\\
\end{tabular*}
\\
\vspace{0.05in}
\rule{6.5in}{2pt}
\\
\vspace{0.10in}
Computer Vision Researcher + Engineer with proven track record of converting research to products. 
%\rule{6.5in}{2pt}
\\
\vspace{0.10in}
{\large \textbf{Experience}}
\begin{itemize*}
\item  
	\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
		\textbf{Staff Research Scientist} at \textbf{Google Research, Mountain View} & \textbf{Oct\textquotesingle 13 - Present} \\
	\end{tabular*}
\\
\begin{flushright}
\begin{flushleft}
	Computer Vision, Machine Learning and Computational Photography. My work forms the basis of Portrait Mode for Google Pixel phones, worked on hand tracking and gesture detection for VR / AR.
\end{flushleft}
\end{flushright}
\vspace{0.03in}
\item  
	\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
		\textbf{Research Engineer} at \textbf{Flutter, (Acquired by Google)} & \textbf{April\textquotesingle 12 - Oct\textquotesingle 13} \\
	\end{tabular*}
\\
\begin{flushright}
\begin{flushleft}
Gesture recognition startup (Mac app rated 4.5+, among Apple's Best Apps of 2012), one of the \textbf{first} employees.
Sped up recognition by $\mathbf{10\times}$,
automated training data collection,
co-invented new state of the art image feature,
developed across OS X, Win, Linux, iOS, Android, Chrome (NaCl and JS).
\end{flushleft}
\end{flushright}
\item  
	\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
		\textbf{Software Engineering Intern} at \textbf{Google Seattle} & \textbf{March\textquotesingle 10 - Sept\textquotesingle 10, June\textquotesingle 11 - Sept\textquotesingle 11} \\
	\end{tabular*}
\\
\begin{flushright}
\begin{flushleft}
	\begin{itemize}
		\item \textbf{Implemented and launched} the \href{http://googlephotos.blogspot.com/2010/08/picasa-38-face-movies-picnik.html}{\emph{Face Movie}} feature included in Picasa 3.8 in just 4 months. Extensively covered in press. \href{http://www.youtube.com/watch?v=fLQtssJDMMc}{Demo video} has 1.5 M+ views on YouTube.
	\item Prototyped an Android app to capture \emph{dynamic mosaics}, an extension of panoramas. 
	\end{itemize}
	\end{flushleft}
\end{flushright}
\item  
	\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
		\textbf{Research Intern} at \textbf{Microsoft Research} & \textbf{June\textquotesingle 08 - Sept\textquotesingle 08, May\textquotesingle 06 - July\textquotesingle 06} \\
	\end{tabular*}
        \textbf{Mentor:} Richard Szeliski / Manik Varma
\\
\begin{flushright}
\begin{flushleft}
	\begin{itemize}
	\item Designed custom features for matching and 3D reconstruction of man made scenes from photos.
	\item Developed locally invariant fractal features for classification of textures (Published at ICCV).
	\end{itemize}
\end{flushleft}
\end{flushright}
%\vspace{0.1in}
%\vspace{2pt}
%\item  
%	\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
%		\textbf{Research Engineer} at \textbf{B-Core Software Pvt. Ltd., New Delhi} & \textbf{June 2007 - Aug 2007} \\
%	\end{tabular*}
%\\
%\vspace{0.1in}
%\vspace{2pt}
%\begin{flushright}
%\begin{flushleft}
%Worked on an image segmentation application for mobile platforms to decode color codes from an image of a colored sequence (analogous to bar codes).
%\end{flushleft}
%\end{flushright}

%\item  
%	\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
%		\textbf{Research Intern} at \textbf{Microsoft Research India} & \textbf{May 2006 - July 2006} \\
%	\end{tabular*}
%\\
%\vspace{0.1in}
%\vspace{2pt}
%\begin{flushright}
%\begin{flushleft}
%  Developed locally invariant fractal features for statistical analysis and classification of textures. Published at ICCV 2007.
%\end{flushleft}
%\end{flushright}
\end{itemize*}
\rule{6.5in}{2pt}
\\
\vspace{0.10in}
{\large \textbf{Education}}

	\begin{itemize*}
	\item
	{
		\begin{tabular*}{6in}{l@{\extracolsep{\fill}}c}
			\textbf{University of Washington}, Seattle, WA & \textbf{2007 - 2012}\\
		\end{tabular*}
	}
		\begin{tabular*}{6in}{l@{\extracolsep{\fill}}c}
                \emph{Ph.D. in Computer Science and Engineering} & \\
                \textbf{Advisor}: Prof. Steven M. Seitz & \\
		\end{tabular*}
	\item
	{
		\begin{tabular*}{6in}{l@{\extracolsep{\fill}}c}
			\textbf{Indian Institute of Technology (IIT) Delhi}, India & \textbf{2003 - 2007} \\
		\end{tabular*}
	}
		\begin{tabular*}{6in}{l@{\extracolsep{\fill}}c}
                  \emph{Bachelor of Technology in Computer Science and Engineering} & \\
                \textbf{GPA: 9.91/10.0, President's Gold Medal}\\
                Highest GPA amongst all outgoing B.Tech. students across all majors\\
                \textbf{All India Rank 7} among 172000 candidates in IIT-Joint Entrance Exam. 2003
		\end{tabular*}
	\end{itemize*}
\rule{6.5in}{2pt}
\\
\vspace{0.10in}
{\large \textbf{Honors and Awards}}
\begin{itemize*}
\item Publications at top-tier vision and graphics conferences (SIGGRAPH, ICCV, CVPR). 10$+$ patents. 
\item Fellowships: NVIDIA Fellowship (2009-10), Clairmont L. Egtvedt Fellowship (2007-08), Weil Family Endowed Fellowship (2007-08), NTSE Scholarship by Govt. of India (2001).
\item Programming Contests: \textbf{Top 12} in TopCoder Open 2008 Marathon competition (\textbf{international} event), \textbf{Top 50} in Google Code Jam India 2006
\end{itemize*}
%\rule{6.5in}{2pt}
\rule{6.5in}{2pt}
\newpage
\rule{6.5in}{2pt}
\\
\vspace{0.10in}
{\large \textbf{Publications}}
\begin{itemize*}
\item S. Niklaus, X. C. Zhang, J. T. Barron, N. Wadhwa, R. Garg, F. Liu, T. Xue, \textbf{Learned Dual-View Reflection Removal}, \emph{WACV, 2021.}
\item Y. Zhang, N. Wadhwa, S. Orts-Escolano, C. H\"ane, S. Fanello, R. Garg, \textbf{Du$^2$Net: Learning Depth Estimation from Dual-Cameras and Dual-Pixels}, \emph{ECCV, 2020.} ({\color{red} Oral. Basis for Portrait Mode on Pixel 4.})
\item C. Herrmann, R. S. Bowen, N. Wadhwa, R. Garg, Q. He, J.T. Barron, R. Zabih, \textbf{Learning to Autofocus}, \emph{CVPR, 2020.} ({\color{red} Basis for low light autofocus on Pixel 5})
\item R. Garg, N. Wadhwa, S. Ansari, J.T. Barron, \textbf{Learning Single Camera Depth Estimation using Dual-Pixels}, \emph{ICCV, 2019.} ({\color{red}Oral. Basis for Portrait Mode on Pixel 3.})
\item S. Ansari, N. Wadhwa, R. Garg, J. Chen, \textbf{Wireless Software Synchronization of Multiple Distributed Cameras}, \emph{ICCP, 2019.}
\item N. Wadhwa, R. Garg, D.E. Jacobs, B.E. Feldman, N. Kanazawa, R. Carroll, Y. Movshovitz-Attias, J.T. Barron, Y. Pritch, M. Levoy, \textbf{Synthetic Depth-of-Field with a Single-Camera Mobile Phone.}, \emph{SIGGRAPH, 2018.} ({\color{red} Basis for Portrait Mode on Pixel 2.})
\item P.P. Srinivasan, R. Garg, N. Wadhwa, R. Ng, J.T. Barron, \textbf{Aperture Supervision for Monocular Depth Estimation}, \emph{CVPR, 2017.}
\item I. Kemelmacher-Shlizerman, E. Shechtman, R. Garg and S.M. Seitz. \textbf{Moving Portraits}, \emph{Communications of ACM, Research Highlights, Sep 2014 (Cover Story).}
\item R. Garg and S.M. Seitz. \textbf{Dynamic Mosaics}, In Proc. of \emph{3D Imaging, Modeling, Processing, Visualization, Transmission Conference (3DIMPVT), 2012}
\item I. Kemelmacher-Shlizerman, E. Shechtman, R. Garg and S.M. Seitz. \textbf{Exploring Photobios}, \emph{SIGGRAPH, 2011}. Featured on SIGGRAPH cover. ({\color{red} Basis for Google Picasa Face Movies feature.})
\item R. Garg, D. Ramanan, S.M. Seitz and N. Snavely. \textbf{Where's Waldo: Matching People in Images of Crowds}, \emph{CVPR, 2011.}
\item R. Garg, H. Du, S.M. Seitz and N. Snavely. \textbf{The Dimensionality of Scene Appearance}, \emph{ICCV, 2009.}
\item N. Snavely, R. Garg, S.M. Seitz and R. Szeliski. \textbf{Finding Paths through the World's Photos}, \emph{SIGGRAPH, 2008.} ({\color{red} Basis for new features in Microsoft's Photosynth.})
\item M. Varma and R. Garg. \textbf{Locally Invariant Fractal Features for Statistical Texture Classification}, \emph{ICCV, 2007.} 
\end{itemize*}
\rule{6.5in}{2pt}
\end{document}
