% resume.tex
%
%
\documentclass[10pt]{article}
\usepackage{fullpage1}	
\usepackage{atbeginend}
\usepackage[pdftex]{hyperref}
\textheight=8.8in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\newenvironment{itemize*}%
  {\begin{itemize}%
    \setlength{\itemsep}{0pt}%
    \setlength{\parskip}{0pt}%
	}
  {\end{itemize}}
\newenvironment{description*}%
  {\begin{description}%
   \setlength{\itemsep}{0pt}%
   \setlength{\parskip}{0pt}%
	}
  {\end{description}}
\begin{document}

\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large{Rahul Garg}}  & \\
Research Engineer &  Ph:(206) 708 5975\\
Flutter Inc. & \href{http://www.cs.washington.edu/homes/rahul}{http://www.rahulgarg.com}\\ 
47, Maiden Lane, San Francisco &  email: \href{mailto:rahul@flutterapp.com}{rahul@flutterapp.com}\\
\end{tabular*}
\\
\vspace{0.05in}
\rule{6.5in}{2pt}
\\
%\vspace{0.10in}
%{\large \textbf{Objective}}
%\\
%\vspace{0.10in}
%Working in a challenging environment involving research in Computer Vision and Graphics

%\\
%\vspace{0.10in}
%\rule{6.5in}{2pt}
%\\
\vspace{0.10in}
{\large \textbf{Education}}

	\begin{itemize*}
	\item
	{
		\begin{tabular*}{6in}{l@{\extracolsep{\fill}}c}
			\textbf{University of Washington}, Seattle, WA & \textbf{2007 - 2012}\\
		\end{tabular*}
	}
		\begin{tabular*}{6in}{l@{\extracolsep{\fill}}c}
                \emph{Ph.D. in Computer Science and Engineering} & \\
                \textbf{Advisor}: Prof. Steven M. Seitz, \textbf{Thesis}: Unstructured Image Mosaics & \\
		\end{tabular*}
	\item
	{
		\begin{tabular*}{6in}{l@{\extracolsep{\fill}}c}
			\textbf{Indian Institute of Technology (IIT) Delhi}, India & \textbf{2003 - 2007} \\
		\end{tabular*}
	}
		\begin{tabular*}{6in}{l@{\extracolsep{\fill}}c}
                  \emph{Bachelor of Technology in Computer Science and Engineering} & \\
                \textbf{GPA: 9.91/10.0, President's Gold Medal}\\
                (Highest GPA amongst all outgoing B.Tech. students across all majors) 
		\end{tabular*}
	\end{itemize*}
%\rule{6.5in}{2pt}
\rule{6.5in}{2pt}
\\
\vspace{0.10in}
{\large \textbf{Honors and Awards}}
\begin{itemize*}
\item \textbf{NVIDIA Fellowship} for the year 2009-2010
\item Among \textbf{top 12} finalists in TopCoder Open 2008 Marathon competition, an \textbf{international} programming contest hosted by www.topcoder.com
\item Among \textbf{top 500} onsite finalists in Google Code Jam 2008 (International event)
\item Recipient of the \textbf{Weil Family Endowed Fellowship} for the year 2007-2008 at the University of Washington
\item Recipient of the \textbf{Clairmont L. Egtvedt Fellowship} awarded by College of Engineering, University of Washington, 2007-2008
\item Among \textbf{top 50} finalists in Google Code Jam India, 2006 (14000 participants from South East Asia)
\item Secured All India \textbf{Rank 7} among 172,000 candidates in IIT-Joint Entrance Examination 2003
\item Secured \textbf{Rank 1} in Common Engineering Test (Delhi) 2003, \textbf{Rank 18} in All India Engineering Entrance Examination 2003
\item Regular member of www.topcoder.com - a website hosting global programming competitions, ranked among \textbf{top 5} in India as an undergraduate
\item Selected for NTSE (National Talent Search Examination) Scholarship awarded by the Govt. of India
\end{itemize*}

\rule{6.5in}{2pt}
\\
\vspace{0.10in}
{\large \textbf{Experience}}
\begin{itemize*}
\item  
	\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
		\textbf{Research Engineer} at \textbf{BotSquare Inc.} & \textbf{June 2012 - Present} \\
	\end{tabular*}
\\
\begin{flushright}
\begin{flushleft}
Building gesture recognition systems.
\end{flushleft}
\end{flushright}
\item  
	\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
		\textbf{Software Engineering Intern} at \textbf{Google Seattle} & \textbf{June 2011 - September 2011} \\
	\end{tabular*}
\\
\begin{flushright}
\begin{flushleft}
Prototyped an Android app that allows the user to take overlapping photos of a scene and browse them in an interactive viewer. A patent was filed for the approach.
\end{flushleft}
\end{flushright}
\item  
	\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
		\textbf{Software Engineering Intern} at \textbf{Google Seattle} & \textbf{March 2010 - September 2010} \\
	\end{tabular*}
\\
\begin{flushright}
\begin{flushleft}
  Implemented the \emph{Face Movie} feature included in Picasa 3.8. Start to launch took 4 months. Patented and extensively covered in press. Demo video has 1.5 million views on Youtube. Thousands of user created face movies uploaded to Youtube.
\end{flushleft}
\end{flushright}
\item  
	\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
		\textbf{Research Intern} at \textbf{Microsoft Research Redmond} & \textbf{June 2008 - September 2008} \\
	\end{tabular*}
\\
\begin{flushright}
\begin{flushleft}
Designed custom features for matching and 3D reconstruction of man made scenes from photos.
\end{flushleft}
\end{flushright}
%\vspace{0.1in}
%\vspace{2pt}
\item  
	\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
		\textbf{Research Engineer} at \textbf{B-Core Software Pvt. Ltd., New Delhi} & \textbf{June 2007 - Aug 2007} \\
	\end{tabular*}
\\
%\vspace{0.1in}
%\vspace{2pt}
\begin{flushright}
\begin{flushleft}
Worked on an image segmentation application for mobile platforms to decode color codes from an image of a colored sequence (analogous to bar codes).
\end{flushleft}
\end{flushright}

\item  
	\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
		\textbf{Research Intern} at \textbf{Microsoft Research India} & \textbf{May 2006 - July 2006} \\
	\end{tabular*}
\\
%\vspace{0.1in}
%\vspace{2pt}
\begin{flushright}
\begin{flushleft}
Developed locally invariant fractal features for statistical analysis and classification of textures. Published at ICCV 2007.
\end{flushleft}
\end{flushright}
\end{itemize*}
\rule{6.5in}{2pt}
\\
\vspace{0.10in}
{\large \textbf{Publications}}
\begin{itemize*}
\item R. Garg and S.M. Seitz. \textbf{Dynamic Mosaics}, In Proc. of \emph{3D Imaging, Modeling, Processing, Visualization, Transmission Conference (3DIMPVT), 2012}
\item I. Kemelmacher-Shlizerman, E. Shechtman, R. Garg and S.M. Seitz. \textbf{Exploring Photobios}, \emph{ACM Transactions on Graphics (Proceedings of SIGGRAPH 2011)}
\item R. Garg, D. Ramanan, S.M. Seitz and N. Snavely. \textbf{Where's Waldo: Matching People in Images of Crowds}, \emph{In Proceedings of IEEE Conference on Computer Vision and Pattern Recognition (CVPR), Colorado Springs, June 2011}
\item R. Garg, H. Du, S.M. Seitz and N. Snavely. \textbf{The Dimensionality of Scene Appearance}, \emph{In Proceedings of the IEEE International Conference on Computer Vision (ICCV), Kyoto, Japan, October 2009}
\item N. Snavely, R. Garg, S.M. Seitz and R. Szeliski. \textbf{Finding Paths through the World's Photos}, \emph{ACM Transactions on Graphics (Proceedings of SIGGRAPH 2008)}
\item M. Varma and R. Garg. \textbf{Locally Invariant Fractal Features for Statistical Texture Classification}, \emph{In Proceedings of the IEEE International Conference on Computer Vision (ICCV), Rio De Janeiro, Brazil, October 2007} 
\end{itemize*}
\rule{6.5in}{2pt}
\\
\vspace{0.10in}
{\large \textbf{Thesis}}
\begin{itemize*}
\item Unstructured Image Mosaics\\
R. Garg, PhD Thesis, Dept. of Computer Science and Engineering, University of Washington, 2012
\end{itemize*}
\begin{itemize*}
\item Locally Invariant Fractal Features for Statistical Texture Classification 
R. Garg, B.Tech Thesis, Dept. of Computer Science and Engineering, IIT Delhi, 2007
\end{itemize*}
\rule{6.5in}{2pt}
\\
\vspace{0.10in}
{\large \textbf{Teaching Experience}}
\begin{itemize*}
\item TA for CSE455 (Undergraduate Computer Vision course) during Winter 2010 at University of Washington.
\item Tutored undergraduate students at University of Washington.
\end{itemize*}
\rule{6.5in}{2pt}
\\
\vspace{0.10in}
{\large \textbf{Talks}}
\begin{itemize*}
\item \textbf{Exploring Photobios} (with Ira Kemelmacher-Shlizerman) 
\\
SIGGRAPH 2011, Vancouver, BC, August 2011.
\item \textbf{Finding Paths through the World's Photos} (with Noah Snavely) 
\\
SIGGRAPH 2008, Los Angeles, CA, August 2008.
\item \textbf{Beyond Photo Tourism: Guided Navigation of Internet Photo Collections} 
\\
Indian Institute of Technology (IIT) Delhi, India, September 2008.
\end{itemize*}
\rule{6.5in}{2pt}
\end{document}
