% resume.tex
%
%
\documentclass[10pt]{article}
\usepackage{fullpage1}	
\usepackage{atbeginend}
\usepackage[pdftex]{hyperref}
\textheight=8.8in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\newenvironment{itemize*}%
  {\begin{itemize}%
    \setlength{\itemsep}{0pt}%
    \setlength{\parskip}{0pt}%
	}
  {\end{itemize}}
\newenvironment{description*}%
  {\begin{description}%
   \setlength{\itemsep}{0pt}%
   \setlength{\parskip}{0pt}%
	}
  {\end{description}}
\begin{document}

\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large{Rahul Garg}}  & \\
Research Engineer &  Ph:(206) 708 5975\\
Botsquare Inc. & \href{http://www.cs.washington.edu/homes/rahul}{http://www.rahulgarg.co}\\ 
47, Maiden Lane, San Francisco &  email: \href{mailto:rahul@botsquare.com}{rahul@botsquare.com}\\
\end{tabular*}
\\
\vspace{0.05in}
\rule{6.5in}{2pt}
\\
%\vspace{0.10in}
%{\large \textbf{Objective}}
%\\
%\vspace{0.10in}
%Working in a challenging environment involving research in Computer Vision and Graphics

%\\
%\vspace{0.10in}
%\rule{6.5in}{2pt}
%\\
\vspace{0.10in}
{\large \textbf{Education}}

	\begin{itemize*}
	\item
	{
		\begin{tabular*}{6in}{l@{\extracolsep{\fill}}c}
			\textbf{University of Washington}, Seattle, WA & \textbf{2007 - 2012}\\
		\end{tabular*}
	}
		\begin{tabular*}{6in}{l@{\extracolsep{\fill}}c}
		Ph.D. in Computer Science and Engineering & \\
		Advisor: Prof. Steven M. Seitz & \\
		\end{tabular*}
	\item
	{
		\begin{tabular*}{6in}{l@{\extracolsep{\fill}}c}
			\textbf{Indian Institute of Technology (IIT) Delhi}, India & \textbf{2003 - 2007} \\
		\end{tabular*}
	}
		\begin{tabular*}{6in}{l@{\extracolsep{\fill}}c}
		Bachelor of Technology in Computer Science and Engineering & \\
		(GPA: 9.91/10.0, President's Gold Medal) 
		\end{tabular*}
	\end{itemize*}
%\rule{6.5in}{2pt}
\rule{6.5in}{2pt}
\\
\vspace{0.10in}
{\large \textbf{Publications}}
\begin{itemize*}
\item R. Garg and S.M. Seitz. \textbf{Dynamic Mosaics}, In Proc. of \emph{3D Imaging, Modeling, Processing, Visualization, Transmission Conference (3DIMPVT), 2012}
\item I. Kemelmacher-Shlizerman, E. Shechtman, R. Garg and S.M. Seitz. \textbf{Exploring Photobios}, \emph{ACM Transactions on Graphics (Proceedings of SIGGRAPH 2011)}
\item R. Garg, D. Ramanan, S.M. Seitz and N. Snavely. \textbf{Where's Waldo: Matching People in Images of Crowds}, \emph{In Proceedings of IEEE Conference on Computer Vision and Pattern Recognition (CVPR), Colorado Springs, June 2011}
\item R. Garg, H. Du, S.M. Seitz and N. Snavely. \textbf{The Dimensionality of Scene Appearance}, \emph{In Proceedings of the IEEE International Conference on Computer Vision (ICCV), Kyoto, Japan, October 2009}
\item N. Snavely, R. Garg, S.M. Seitz and R. Szeliski. \textbf{Finding Paths through the World's Photos}, \emph{ACM Transactions on Graphics (Proceedings of SIGGRAPH 2008)}
\item M. Varma and R. Garg. \textbf{Locally Invariant Fractal Features for Statistical Texture Classification}, \emph{In Proceedings of the IEEE International Conference on Computer Vision (ICCV), Rio De Janeiro, Brazil, October 2007} 
\end{itemize*}
\rule{6.5in}{2pt}
\\
\vspace{0.10in}
{\large \textbf{Employment}}
\begin{itemize*}
\item  
	\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
		\textbf{Research Engineer} at \textbf{BotSquare Inc.} & \textbf{June 2012 - Present} \\
	\end{tabular*}
\\
\begin{flushright}
\begin{flushleft}
Building gesture recognition systems.
\end{flushleft}
\end{flushright}
\item  
	\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
		\textbf{Software Engineering Intern} at \textbf{Google Seattle} & \textbf{June 2011 - September 2011} \\
	\end{tabular*}
\\
\textbf{Mentor}: Prof. Steven M. Seitz%, Microsoft Research India
\begin{flushright}
\begin{flushleft}
Prototyped an Android app that allows the user to take overlapping photos of a scene and browse them in an interactive viewer. A patent was filed for the approach.
\end{flushleft}
\end{flushright}
\item  
	\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
		\textbf{Software Engineering Intern} at \textbf{Google Seattle} & \textbf{March 2010 - September 2010} \\
	\end{tabular*}
\\
\textbf{Mentor}: Prof. Steven M. Seitz%, Microsoft Research India
\begin{flushright}
\begin{flushleft}
Implemented the Face Movie feature included in personal photo organizer software Picasa 3.8. Patented and extensively covered in press. Demo video has 1.5 M views on Youtube.
\end{flushleft}
\end{flushright}
\item  
	\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
		\textbf{Research Intern} at \textbf{Microsoft Research Redmond} & \textbf{June 2008 - September 2008} \\
	\end{tabular*}
\\
\textbf{Mentor}: Dr. Richard  Szeliski%, Microsoft Research India
\begin{flushright}
\begin{flushleft}
Worked on the problem of detecting and matching features across images of man made scenes.
\end{flushleft}
\end{flushright}
%\vspace{0.1in}
%\vspace{2pt}
\item  
	\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
		\textbf{Research Engineer} at \textbf{B-Core Software Pvt. Ltd., New Delhi} & \textbf{June 2007 - Aug 2007} \\
	\end{tabular*}
\\
%\vspace{0.1in}
%\vspace{2pt}
\begin{flushright}
\begin{flushleft}
Worked on an application for mobile platforms to decode color codes from an image of a colored sequence (analogous to bar codes).
\end{flushleft}
\end{flushright}

\item  
	\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
		\textbf{Research Intern} at \textbf{Microsoft Research India} & \textbf{May 2006 - July 2006} \\
	\end{tabular*}
\\
%\vspace{0.1in}
\textbf{Mentor}: Dr. Manik Varma%, Microsoft Research India
%\vspace{2pt}
\begin{flushright}
\begin{flushleft}
Developed locally invariant fractal features which allow for statistical analysis and classification of textures.
\end{flushleft}
\end{flushright}
\item
	\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
		\textbf{Summer Internship} at \textbf{IIT, Delhi} & \textbf{May 2005 - July 2005} \\
	\end{tabular*}
\\
%\vspace{0.1in}
\textbf{Mentor}: Prof. Subhashis Banerjee%, Department of Computer Science and Engineering, IIT Delhi  
%\vspace{0.05in}
\begin{flushleft}
Developed method to automatically detect vehicles in a video stream. Recipient of prestigious \textbf{SURA} (Summer Undergraduate Research Award), 2005 awarded by Industrial Research and Development Unit (IRD), IIT Delhi.
\end{flushleft}
\end{itemize*}
\rule{6.5in}{2pt}
\\
\vspace{0.10in}
{\large \textbf{Thesis}}
\begin{itemize*}
\item Unstructured Image Mosaics\\
R. Garg, PhD Thesis, Dept. of Computer Science and Engineering, University of Washington, 2012
\end{itemize*}
\begin{itemize*}
\item Locally Invariant Fractal Features for Statistical Texture Classification 
R. Garg, B.Tech Thesis, Dept. of Computer Science and Engineering, IIT Delhi, 2007
\end{itemize*}
\rule{6.5in}{2pt}
\\
\vspace{0.10in}
{\large \textbf{Teaching Experience}}
\begin{itemize*}
\item TA for CSE455 (Undergraduate Computer Vision course) during Winter 2010 at University of Washington.
\item Tutored undergraduate students at University of Washington.
\end{itemize*}
\rule{6.5in}{2pt}
\\
\vspace{0.10in}
{\large \textbf{Talks}}
\begin{itemize*}
\item \textbf{Exploring Photobios} (with Ira Kemelmacher-Shlizerman) 
\\
SIGGRAPH 2011, Vancouver, BC, August 2011.
\item \textbf{Finding Paths through the World's Photos} (with Noah Snavely) 
\\
SIGGRAPH 2008, Los Angeles, CA, August 2008.
\item \textbf{Beyond Photo Tourism: Guided Navigation of Internet Photo Collections} 
\\
Indian Institute of Technology (IIT) Delhi, India, September 2008.
\end{itemize*}
\rule{6.5in}{2pt}
\\
\vspace{0.10in}
{\large \textbf{Academic Achievements}}
\begin{itemize*}
\item Recipient of \textbf{NVIDIA Fellowship} for the year 2009-2010.
\item Recipient of the \textbf{Weil Family Endowed Fellowship} for the year 2007-2008 at the University of Washington
\item Recipient of the \textbf{Clairmont L. Egtvedt Fellowship} awarded by College of Engineering, University of Washington, 2007-2008
\item Awarded  the \textbf{President of India Gold Medal} for securing the highest cumulative GPA among all outgoing B.Tech. students  across all disciplines in 2007 batch, IIT Delhi
\item Secured All Indian \textbf{Rank 7} among 172,000 candidates in IIT-Joint Entrance Examination 2003
\item Secured \textbf{Rank 1} in Common Engineering Test (Delhi) 2003, \textbf{Rank 18} in All India Engineering Entrance Examination 2003
\item Selected for NTSE (National Talent Search Examination) Scholarship awarded by the Govt. of India
\item Selected for Training Camp, Indian  National Physics Olympiad 2003
\item Awards in many mathematics contests - RMO (Regional Mathematics Olympiad), SMO (Senior Mathematics Olympiad), etc.
\end{itemize*}


\rule{6.5in}{2pt}
\\
{\large \textbf{Programming Competitions}}
\begin{itemize*}
  \item Among \textbf{top 12} finalists in TopCoder Open 2008 Marathon competition, an \textbf{international} event hosted by www.topcoder.com. 
  \item Among \textbf{top 500} onsite finalists in Google Code Jam 2008, an \textbf{international} programming contest organized by Google.
  \item Among \textbf{top 50} finalists in Google Code Jam India, 2006 - Programming Contest organized by Google which attracted over 14,000 participants from South East Asia.
  \item Problem setter for International Online Programming Contest organized during Tryst 2007, the technical festival of IIT Delhi. 
  \item Represented IIT Delhi in ACM International Collegiate Programming Contest 2007. 
  \item Regular member of www.topcoder.com - a website hosting global programming competitions, ranked among \textbf{top 5} in India as an undergraduate.
\end{itemize*}

\rule{6.5in}{2pt}
\end{document}
